Proposed Solution

### 2016-05-08 CAV/evaluation.tex
config: cav paper

\app is implemented in Haskell and takes full advantage of its polymorphism to make the system more modular.
In particular, rules are represented as a type, where the type must support a particular interface (called a typeclass in Haskell) to be compatible with our system.
By using language extensions (FlexibleInstances and MultiParamTypeClasses), this typeclass can be made polymorphic over the data structure as denoted by \lstinline{Foldable t =>}.
The user can then choose a data structure that is most natural to the rule they are implementing.
For example, in our implementation, Missing Entries were easier to manipulate in lists, while Type Errors fit more naturally into a hashmap.
This typeclass defines the three functions that each set of rules must implement to work with our system. The core learning algorithm is simply a fold using \lstinline{merge} over the derived rules from running \lstinline{learn} on each file in the learning set.

@@

The integer relation rule has an unusual implementation that makes use of function as first-class objects in Haskell.
Rather than associated keywords with SMT formula, we directly associate them with a function of type (\lstinline{Int->Int->Bool}).
Since we need to compare rules over equality, we must then have a way to compare functions.
This limits the types of functions we use to \lstinline{(==),(>=),(<=)}.
Although this is sufficient for most use cases, more fine-grained relations could be encoded with SMT formulas then passed to a solver.

@@

\subsection{Evaluation}

To evaluate our tool, we take a subset of 20 benchmarks from an
existing dataset of configuration errors~\cite{yin11anempirical,xu15hey,configdataset} which are supported by our tool. Table~\ref{table:res} contains an evaluation summary.
We do not report the running times, since they are negligible: even when
 running in the interpreter mode, files are analyzed instantaneously. We
spent approximately 30 second on learning the rules. When we run the
compiled version, we need for learning and verification 
combined less than 5 seconds. Our focus is usefulness of the tool: its 
 ability to detect configuration errors and the number of false positives.
 For every benchmark class we took five examples. The middle column represents the number of detected errors, while the right column represents the number of returned false positives per each benchmark.

@@

\begin{table}[t]
\centering
\caption{Benchmarks for misconfiguration detection}
\label{table:res}
\begin{tabular}{l|l|l}
Error Type       & Passing Tests & False Positives  \\ \hhline{=|=|=}
Missing Entry    & 5/5           & 1, 0, 0, 0, 4        \\ \hline
Type Error       & 5/5           & 0, 0, 0, 0, 0          \\ \hline
Keyword Ordering & 5/5           & 0, 2, 1, 0, 6       \\ \hline
Value Relations  & 4/5           & 0, 0, 0, 1, 0        \\ 
\end{tabular}
\end{table}
%\vspace{-5em}

>>>>

\para{Implementation.}
\app is implemented in Haskell and takes full advantage of its polymorphism to make the system more modular.
In particular, rules are represented as a type, where the type must support a particular interface (called a typeclass in Haskell) to be compatible with our system.
By using language extensions (FlexibleInstances and MultiParamTypeClasses), this typeclass can be made polymorphic over the data structure as denoted by \lstinline{Foldable t =>}.
The user can then choose a data structure that is most natural to the rule they are implementing.
For example, in our implementation, Missing Entries were easier to manipulate in lists, while Type Errors fit more naturally into a hashmap.
This typeclass defines the three functions that each set of rules must implement to work with our system. The core learning algorithm is simply a fold using \lstinline{merge} over the derived rules from running \lstinline{learn} on each file in the learning set.

@@

The integer relation rule has an unusual implementation that uses function as first-class objects in Haskell.
Rather than associated keywords with SMT formula, we directly associate them with a function of type (\lstinline{Int->Int->Bool}).
Since we need to compare rules over equality, we must have a way to compare functions.
This limits the types of functions we use to \lstinline{(==),(>=),(<=)}.
Although this is sufficient for most cases, more fine-grained relations could be encoded with SMT formulas then passed to a solver.

@@

\para{Evaluation.}
To evaluate our tool, we take a subset of 20 benchmarks from an
existing dataset of configuration errors~\cite{yin11anempirical,xu15hey,configdataset} which are supported by our tool. Table~\ref{table:res} contains an evaluation summary.
We do not report the running times, since they are negligible: even when
 running in the interpreter mode, files are analyzed instantaneously. We
spent approximately 30 second on learning the rules. When we run the
compiled version, we need for learning and verification 
combined less than 5 seconds. Our focus is usefulness of the tool: its 
 ability to detect configuration errors and the number of false positives.
 For every benchmark class we took five examples. The middle column represents the number of detected errors, while the right column represents the number of returned false positives per each benchmark.

@@

\begin{table}[t]
\centering
\caption{Benchmarks for misconfiguration detection}
\label{table:res}
\begin{tabular}{|l|l|l|}
\hline
Error Type       & Passing Tests & False Positives  \\ 
\hline
\hline
Missing Entry    & 5/5           & 1, 0, 0, 0, 4        \\ \hline
Type Error       & 5/5           & 0, 0, 0, 0, 0          \\ \hline
Keyword Ordering & 5/5           & 0, 2, 1, 0, 6       \\ \hline
Value Relations  & 4/5           & 0, 0, 0, 1, 0        \\ 
\hline
\end{tabular}
\end{table}

### 2016-05-08 CAV/intro1.tex
?
config: cav paper

We propose an approach to the verification of  
configuration files which is based on learning rules about the language 
model for configuration files.

\begin{figure}[t] \centering
\includegraphics[width=0.63\textwidth]{figs/overview}
\caption{{\footnotesize \app's workflow. The green boxes represent configuration files,
  including both correct general configuration files and users' input
  configuration files. The purple boxes are the components within \app.
  The yellow boxes are results generated by \app's components.}}
\label{fig-overview}
\end{figure}

Figure~\ref{fig-overview} describes an overview of our system. We start
with the assumption that we are given a number of correct configuration
files belonging to the same category (for instance, MySQL or
Apache). Such files follow similar patterns, which we exploit
in a learning algorithm to build rules that
describe a language model for the files. Since the
``language'' of configuration types is untyped and unstructured, we
first parse the files and translate them into a more structured,
intermediary representation.
When running type inference on a configuration file, the type of a variable cannot always be fully determined from a single value.
We address this problem by introducing so called {\emph{probabalistic types}}.
Rather than giving a variable a single type, we assign several types with their probability distributions. 
We can then use these more structured files
as a training set to learn the rules. The learning algorithm
is template-based to be easily extensible. We provide an initial set of templates and the
learner learns some concrete instances from the training set. These
rules are used for detecting errors violating the learned constraints
in the files given by the user.

@@

To summarize, this tool paper makes the following contributions:

\begin{enumerate}

  \item We designed and implemented a tool, \app, that can learn a
language model from an example set of correct configuration files, and
we use the model to verify new configuration files.
  \item We use probabilistic types to assign a confidence distribution over a set of types to a value.
  \item In \app we define a interface for describing a verification attribute in a learning context, making it easy to add new rules to the system.

\end{enumerate}

>>>>

We propose an approach to the verification of  
configuration files which is based on learning rules about the language 
model for configuration files. 
There is no universal definition of a "configuration file". In general, most configuration files tend to be a series of assignment to system variables. Configuration files generally do not have more complicated language constructs, lest they become a setup script.

{
\setlength{\floatsep}{-10pt}
\setlength{\abovecaptionskip}{-.5pt}
\setlength{\belowcaptionskip}{-14pt}
\begin{figure}[t] \centering
\includegraphics[width=0.6\textwidth]{figs/overview}
\caption{{\footnotesize \app's workflow. The green boxes represent configuration files,
  including both correct general configuration files and users' input
  configuration files. The purple boxes are the components within \app.
  The yellow boxes are results generated by \app's components.}}
\label{fig-overview}
\end{figure}
}

Figure~\ref{fig-overview} describes an overview of our system. We start
with the assumption that we are given a number of correct configuration
files belonging to the same category (for instance, MySQL or
Apache). Such files follow similar patterns, which we exploit
in a learning algorithm to build rules that
describe a language model for the files. Since the
``language'' of configuration types is untyped and unstructured, we
first parse the files and translate them into a more structured,
intermediary representation.
When running type inference on a configuration file, the type of a variable cannot always be fully determined from a single value.
We address this problem by introducing so called {\emph{probabilistic types}}.
Rather than giving a variable a single type, we assign several types with their probability distributions. 
We can then use these more structured files
as a training set to learn the rules. The learning algorithm
is template-based to be easily extensible. We provide an initial set of templates and the
learner learns some concrete instances from the training set. These
rules are used for detecting errors violating the learned constraints
in the files given by the user.

@@

To summarize, this tool paper makes the following contributions.
First, we designed and implemented a tool, \app, that can learn a
language model from an example set of correct configuration files, and
we use the model to verify new configuration files.
Second, we use probabilistic types to assign a confidence distribution over a set of types to a value.
Finally, in \app we define a interface for describing a verification attribute in a learning context, making it easy to add new rules to the system.

### 2016-05-08 CAV/system.tex
config: cav paper

To learn rules, we first translate to the intermediate representation where each line of a configuration file is reduced to a keyword-value pair $(k,v)$.
Parsing is language dependent and users may provide extra help to the translator for their specific language, such as specifying a comment character.
We must assign types to the keywords to guide the learning modules. 
With typed keyword-value pairs, we can run each learning module independent of each other.
We learn a set of rules over a every file, then merge the rules of all files.

{\bf {Introducing the types.}} Based only on a single example value of $v$ we cannot fully determine the type of $k$.
Consider for instance the following example:\\
\texttt{\hspace*{2em}foo = 300\\
\hspace*{2em}bar = 300.txt}\\
Most likely \texttt{foo} is an integer and we learn an equality rule, but it could also be a string.
In this case we want to learn the rule $ \texttt{foo} \in \textsf{substrings}(\texttt{bar})$. 
We therefore assign a distribution of types to a value, an idea closely related to existentially quantified types \cite{Launchbury93lazyfunctional}. We introduce {\emph{probabilistic types}} to address this issue.

@@

{\bf {Rule Learning.}} With every type we associate a set of templates, specific to this type. Once the input files are fully type-annotated, we generate rules that are instances of these templates. We always learn the largest set of rules that all correct configuration files satisfy. This way \app can guarantee that, over the set of rules we consider, there will be no false negatives that could have been caught with the given learning set. The only case of a false negative can be when there was no evidence of such a rule in the learning set - we cannot generate rules from nothing. 
%Framed as the question "Is this file valid", \app is complete but not sound

>>>>

To learn rules, we first translate to the intermediate representation where each line of a configuration file is reduced to a keyword-value pair $(k,v)$.
Parsing is language dependent and users may provide extra help to the translator for their specific language, such as specifying a comment character.
We must assign types to the keywords to guide the learning modules. 
With typed keyword-value pairs, we can run each learning module independent of each other.
We learn a set of rules over every file, then merge them.

\para{Introducing the types.} 
Based only on a single example value of $v$ we cannot fully determine the type of $k$.
Consider for instance the following example:\\
\texttt{\hspace*{2em}foo = 300\\
\hspace*{2em}bar = 300.txt}\\
Most likely \texttt{foo} is an integer and we learn an equality rule, but it could also be a string.
In this case we want to learn the rule $ \texttt{foo} \in \textsf{substrings}(\texttt{bar})$. 
We therefore assign a distribution of types to a value, an idea closely related to existentially quantified types \cite{Launchbury93lazyfunctional}. We introduce {\emph{probabilistic types}} to address this issue.

@@

\para{Rule Learning.} 
With every type we associate a set of templates, specific to this type. Once the input files are fully type-annotated, we generate rules that are instances of these templates. We always learn the largest set of rules that all correct configuration files satisfy. This way \app can guarantee that, over the set of rules we consider, there will be no false negatives that could have been caught with the given learning set. The only case of a false negative can be when there was no evidence of such a rule in the learning set - we cannot generate rules from nothing. 
%Framed as the question "Is this file valid", \app is complete but not sound
